---
title: "Exploration"
author: "Amber Thomas"
date: "3/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Looking at the data on repeat models

```{r}
library(here)
library(tidyverse)
library(lubridate)
```

```{r}
faces <- read.csv("../src/assets/data/faces.csv", header = TRUE, stringsAsFactors = FALSE)
models <- read.csv("../src/assets/data/models.csv", header = TRUE, stringsAsFactors = FALSE)
```

Anything interesting when comparing lightness value to number of covers? 
```{r}
ggplot(models, aes(x = l, y = n_covers)) + geom_point()
```

Anything different if we look at woc? 

```{r}
ggplot(models, aes(x = l, y = n_covers)) + geom_point() + facet_wrap(~woc)
```

Average number of covers by woc? 

```{r}
models %>% 
  group_by(woc) %>% 
  summarise(mean = mean(n_covers))
```

What percent of white vs. woc are on the cover more than once? 

```{r}
models %>% 
  group_by(woc) %>% 
  mutate(total = n()) %>% 
  mutate(mult = ifelse(n_covers > 1, "y", "n")) %>% 
  group_by(woc, mult) %>% 
  summarise(per = n() )
```

Difference in if there is a repeat, how many repeats? 

```{r}
models %>% 
  filter(n_covers > 1) %>% 
  group_by(woc) %>% 
  summarise(mean = mean(n_covers))
```

big difference in the time span specific models have been showing up? 

```{r}
faces %>% 
  mutate(date = mdy(date)) %>% 
  group_by(model) %>% 
  arrange(date) %>% 
  mutate(count = n()) 
```

finding file name for cover instead of face
```{r}
coverfiles <- faces %>% 
  mutate(faceFile = file_name) %>% 
  separate(file_name, c("string", "ext"), "\\.") %>% 
  mutate(newString = stringr::str_sub(string, end = -3)) %>% 
  mutate(coverFile = paste0(newString, ".", ext)) %>% 
  select(-c("string", "ext", "newString")) %>% 
  rename(file_name = faceFile)

write.csv(coverfiles, "../src/assets/data/faces.csv", row.names = FALSE)
```

```{r}
models %>% filter(n_covers > 1)
```
```{r}
repeats <- faces %>% 
  mutate(date = mdy(date),
         year = year(date)) %>% 
  filter(year >= 2014) %>% 
  group_by(woc, model) %>% 
  summarise(count = n()) %>% 
  filter(count >= 2) %>% 
  group_by(woc) %>% 
  summarise(count = n())
```


```{r}
unique <- faces %>% 
  group_by(coverFile) %>% 
  mutate(count = n()) %>% 
  filter(count == 1) %>% 
  distinct(coverFile, .keep_all = TRUE) %>% 
  distinct(model, .keep_all = TRUE)

sub <- unique[sample(nrow(unique)),] %>% 
  head(., n = 40)

write.csv(sub, "../src/assets/data/unique.csv", row.names = FALSE)
```

